```{r item_preparation, include=FALSE}

# Item preparation
source("scripts/item_preparation.R")

# Read images
# Fact-box
# Directory
fact_box_dir <- "materials/Presentation_format/fbpi/output/"
# Fact-box img files
fact_box_imgs <- dir(fact_box_dir)

# New paradigm
# Directory
new_paradigm_dir <- "materials/Presentation_format/nppi/output/"
# Fact-box img files
new_paradigm_imgs <- dir(new_paradigm_dir)

# Function for displaying items
source("functions/print_cat_items.R")
source("functions/remove_placeholders.R")
source("functions/asterik_name_remover.R")

```

```{r, down_img, echo=FALSE}
# Download pictorial items images
img_urls <-
  read_csv("materials/img_url.csv", col_types = cols(), col_names = c("condition", "url"))

img_urls$condition %>%
  walk(~download.file(img_urls$url[img_urls$condition == .x], paste0("materials/downloaded_img/", .x, ".png")))
```

```{r}
# function to display items
source("functions/display_items.R")
```


# Breast Cancer Items

## Low normative PPV

### NF ABSOLUTE

```{r, results='asis', echo=FALSE, ca_nfab_low}
display_item(c("ca", "nfab", "low", "gi"))
display_item(c("ca", "nfab", "low", "gs"))
display_item(c("ca", "nfab", "low", "sg"))
display_item(c("ca", "nfab", "low", "ss"))
```

### PR ABSOLUTE

```{r, results='asis', echo=FALSE, ca_prab_low}
display_item(c("ca", "prab", "low", "gi"))
display_item(c("ca", "prab", "low", "gs"))
display_item(c("ca", "prab", "low", "sg"))
display_item(c("ca", "prab", "low", "ss"))
```

### PR RELATIVE

```{r, results='asis', echo=FALSE, ca_prre_low}
display_item(c("ca", "prre", "low", "gi"))
display_item(c("ca", "prre", "low", "gs"))
display_item(c("ca", "prre", "low", "sg"))
display_item(c("ca", "prre", "low", "ss"))
```

### PF ABSOLUTE

```{r, results='asis', echo=FALSE, ca_pfab_low}
display_item(c("ca", "pfab", "low", "gi"))
display_item(c("ca", "pfab", "low", "gs"))
display_item(c("ca", "pfab", "low", "sg"))
display_item(c("ca", "pfab", "low", "ss"))
```

### FB PICTORIAL

```{r, results='asis', echo=FALSE, ca_fbpi_low}
display_item(c("ca", "fbpi", "low", "gi"))
display_item(c("ca", "fbpi", "low", "gs"))
display_item(c("ca", "fbpi", "low", "sg"))
display_item(c("ca", "fbpi", "low", "ss"))
```

### NP PICTORIAL

```{r, results='asis', echo=FALSE, ca_nppi_low}
display_item(c("ca", "nppi", "low", "gi"))
display_item(c("ca", "nppi", "low", "gs"))
display_item(c("ca", "nppi", "low", "sg"))
display_item(c("ca", "nppi", "low", "ss"))
```

## High normative PPV

### NF ABSOLUTE

```{r, results='asis', echo=FALSE, ca_nfab_high}
display_item(c("ca", "nfab", "high", "gi"))
display_item(c("ca", "nfab", "high", "gs"))
display_item(c("ca", "nfab", "high", "sg"))
display_item(c("ca", "nfab", "high", "ss"))
```

### PR ABSOLUTE

```{r, results='asis', echo=FALSE, ca_prab_high}
display_item(c("ca", "prab", "high", "gi"))
display_item(c("ca", "prab", "high", "gs"))
display_item(c("ca", "prab", "high", "sg"))
display_item(c("ca", "prab", "high", "ss"))
```

### PR RELATIVE

```{r, results='asis', echo=FALSE, ca_prre_high}
display_item(c("ca", "prre", "high", "gi"))
display_item(c("ca", "prre", "high", "gs"))
display_item(c("ca", "prre", "high", "sg"))
display_item(c("ca", "prre", "high", "ss"))
```

### PF ABSOLUTE

```{r, results='asis', echo=FALSE, ca_pfab_high}
display_item(c("ca", "pfab", "high", "gi"))
display_item(c("ca", "pfab", "high", "gs"))
display_item(c("ca", "pfab", "high", "sg"))
display_item(c("ca", "pfab", "high", "ss"))
```

### FB PICTORIAL

```{r, results='asis', echo=FALSE, ca_fbpi_high}
display_item(c("ca", "fbpi", "high", "gi"))
display_item(c("ca", "fbpi", "high", "gs"))
display_item(c("ca", "fbpi", "high", "sg"))
display_item(c("ca", "fbpi", "high", "ss"))
```

### NP PICTORIAL

```{r, results='asis', echo=FALSE, ca_nppi_high}
display_item(c("ca", "nppi", "high", "gi"))
display_item(c("ca", "nppi", "high", "gs"))
display_item(c("ca", "nppi", "high", "sg"))
display_item(c("ca", "nppi", "high", "ss"))
```

# Trisomy 21 Items

## Low normative PPV

### NF ABSOLUTE

```{r, results='asis', echo=FALSE, pr_nfab_low}
display_item(c("pr", "nfab", "low", "gi"))
display_item(c("pr", "nfab", "low", "gs"))
display_item(c("pr", "nfab", "low", "sg"))
display_item(c("pr", "nfab", "low", "ss"))
```

### PR ABSOLUTE

```{r, results='asis', echo=FALSE, pr_prab_low}
display_item(c("pr", "prab", "low", "gi"))
display_item(c("pr", "prab", "low", "gs"))
display_item(c("pr", "prab", "low", "sg"))
display_item(c("pr", "prab", "low", "ss"))
```

### PR RELATIVE

```{r, results='asis', echo=FALSE, pr_prre_low}
display_item(c("pr", "prre", "low", "gi"))
display_item(c("pr", "prre", "low", "gs"))
display_item(c("pr", "prre", "low", "sg"))
display_item(c("pr", "prre", "low", "ss"))
```

### PF ABSOLUTE

```{r, results='asis', echo=FALSE, pr_pfab_low}
display_item(c("pr", "pfab", "low", "gi"))
display_item(c("pr", "pfab", "low", "gs"))
display_item(c("pr", "pfab", "low", "sg"))
display_item(c("pr", "pfab", "low", "ss"))
```

### FB PICTORIAL

```{r, results='asis', echo=FALSE, pr_fbpi_low}
display_item(c("pr", "fbpi", "low", "gi"))
display_item(c("pr", "fbpi", "low", "gs"))
display_item(c("pr", "fbpi", "low", "sg"))
display_item(c("pr", "fbpi", "low", "ss"))
```

### NP PICTORIAL

```{r, results='asis', echo=FALSE, pr_nppi_low}
display_item(c("pr", "nppi", "low", "gi"))
display_item(c("pr", "nppi", "low", "gs"))
display_item(c("pr", "nppi", "low", "sg"))
display_item(c("pr", "nppi", "low", "ss"))
```

## High normative PPV

### NF ABSOLUTE

```{r, results='asis', echo=FALSE, pr_nfab_high}
display_item(c("pr", "nfab", "high", "gi"))
display_item(c("pr", "nfab", "high", "gs"))
display_item(c("pr", "nfab", "high", "sg"))
display_item(c("pr", "nfab", "high", "ss"))
```

### PR ABSOLUTE

```{r, results='asis', echo=FALSE, pr_prab_high}
display_item(c("pr", "prab", "high", "gi"))
display_item(c("pr", "prab", "high", "gs"))
display_item(c("pr", "prab", "high", "sg"))
display_item(c("pr", "prab", "high", "ss"))
```

### PR RELATIVE

```{r, results='asis', echo=FALSE, pr_prre_high}
display_item(c("pr", "prre", "high", "gi"))
display_item(c("pr", "prre", "high", "gs"))
display_item(c("pr", "prre", "high", "sg"))
display_item(c("pr", "prre", "high", "ss"))
```

### PF ABSOLUTE

```{r, results='asis', echo=FALSE, pr_pfab_high}
display_item(c("pr", "pfab", "high", "gi"))
display_item(c("pr", "pfab", "high", "gs"))
display_item(c("pr", "pfab", "high", "sg"))
display_item(c("pr", "pfab", "high", "ss"))
```

### FB PICTORIAL

```{r, results='asis', echo=FALSE, pr_fbpi_high}
display_item(c("pr", "fbpi", "high", "gi"))
display_item(c("pr", "fbpi", "high", "gs"))
display_item(c("pr", "fbpi", "high", "sg"))
display_item(c("pr", "fbpi", "high", "ss"))
```

### NP PICTORIAL

```{r, results='asis', echo=FALSE, pr_nppi_high}
display_item(c("pr", "nppi", "high", "gi"))
display_item(c("pr", "nppi", "high", "gs"))
display_item(c("pr", "nppi", "high", "sg"))
display_item(c("pr", "nppi", "high", "ss"))
```

# Comprehension questions

```{r comprehension, echo=FALSE, results='asis'}
source("scripts/comprehension_preparing.R")

invisible(lapply(comprehension_questions, lapply, cat))
```


# Follow-up questions

```{r follow-up, echo=FALSE, results='asis'}
# Create follow-up --------------------------------------------------------
source("scripts/followUp_create_export.R")

```


# Scales

```{r scales, echo=FALSE, results='asis'}
source("scripts/scales_preparing.R")
```

# Item export

```{r}
source("scripts/complete_export_qualtrics.R")
```

