# FINAL ITEMS

## Dictionary

* Problems context:
    + ca: breast cancer
    + pr: pregnant trisomy 21
* Presentation format:
    + nfab: Natural Frequency absolute
    + prab: Probability absolute
    + prre: Probability relative
    + pf: Positive framework
* Normative PPV:
    + low: low ppv (33%)
    + high: high ppv (66%)
* Response type:
    + gi: global intuitive
    + gs: global systematic
    + sg: sequential guided
    + ss: sequential simple
    
## Breast Cancer

### Low normative PPV

#### NF ABSOLUTE

```{r, results='asis', echo=FALSE, ca_nfab_low}
invisible(lapply(items_to_use_responses[grep("ca_nfab_low", items_to_use_responses)], function(x) cat(x, sep = "\n****************************\n")))
```

#### PR ABSOLUTE

```{r, results='asis', echo=FALSE, ca_prab_low}
invisible(lapply(items_to_use_responses[grep("ca_prab_low", items_to_use_responses)], function(x) cat(x, sep = "\n****************************\n")))
```

#### PR RELATIVE

```{r, results='asis', echo=FALSE, ca_prre_low}
invisible(lapply(items_to_use_responses[grep("ca_prre_low", items_to_use_responses)], function(x) cat(x, sep = "\n****************************\n")))
```

#### PF

```{r, results='asis', echo=FALSE, ca_pf_low}
invisible(lapply(items_to_use_responses[grep("ca_pf_low", items_to_use_responses)], function(x) cat(x, sep = "\n****************************\n")))
```

### High normative PPV

#### NF ABSOLUTE

```{r, results='asis', echo=FALSE, ca_nfab_high}
invisible(lapply(items_to_use_responses[grep("ca_nfab_high", items_to_use_responses)], function(x) cat(x, sep = "\n****************************\n")))
```

#### PR ABSOLUTE

```{r, results='asis', echo=FALSE, ca_prab_high}
invisible(lapply(items_to_use_responses[grep("ca_prab_high", items_to_use_responses)], function(x) cat(x, sep = "\n****************************\n")))
```

#### PR RELATIVE

```{r, results='asis', echo=FALSE, ca_prre_high}
invisible(lapply(items_to_use_responses[grep("ca_prre_high", items_to_use_responses)], function(x) cat(x, sep = "\n****************************\n")))
```

#### PF

```{r, results='asis', echo=FALSE, ca_pf_high}
invisible(lapply(items_to_use_responses[grep("ca_pf_high", items_to_use_responses)], function(x) cat(x, sep = "\n****************************\n")))

```


***********************
## Trisomy 21

### Low normative PPV

#### NF ABSOLUTE

```{r, results='asis', echo=FALSE, pr_nfab_low}
invisible(lapply(items_to_use_responses[grep("pr_nfab_low", items_to_use_responses)], function(x) cat(x, sep = "\n****************************\n")))
```

#### PR ABSOLUTE

```{r, results='asis', echo=FALSE, pr_prab_low}
invisible(lapply(items_to_use_responses[grep("pr_prab_low", items_to_use_responses)], function(x) cat(x, sep = "\n****************************\n")))
```

#### PR RELATIVE

```{r, results='asis', echo=FALSE, pr_prre_low}
invisible(lapply(items_to_use_responses[grep("pr_prre_low", items_to_use_responses)], function(x) cat(x, sep = "\n****************************\n")))
```

#### PF

```{r, results='asis', echo=FALSE, pr_pf_low}
invisible(lapply(items_to_use_responses[grep("pr_pf_low", items_to_use_responses)], function(x) cat(x, sep = "\n****************************\n")))
```

### High normative PPV

#### NF ABSOLUTE

```{r, results='asis', echo=FALSE, pr_nfab_high}
invisible(lapply(items_to_use_responses[grep("pr_nfab_high", items_to_use_responses)], function(x) cat(x, sep = "\n****************************\n")))
```

#### PR ABSOLUTE

```{r, results='asis', echo=FALSE, pr_prab_high}
invisible(lapply(items_to_use_responses[grep("pr_prab_high", items_to_use_responses)], function(x) cat(x, sep = "\n****************************\n")))
```

#### PR RELATIVE

```{r, results='asis', echo=FALSE, pr_prre_high}
invisible(lapply(items_to_use_responses[grep("pr_prre_high", items_to_use_responses)], function(x) cat(x, sep = "\n****************************\n")))
```

#### PF

```{r, results='asis', echo=FALSE, pr_pf_high}
invisible(lapply(items_to_use_responses[grep("pr_pf_high", items_to_use_responses)], function(x) cat(x, sep = "\n****************************\n")))
```

*************************
## Pictorial presentation formats

### Fact-box item

```{r, echo=FALSE, results='asis'} 
img_fact <- readPNG("materials/Presentation format/Fact-boxs/fact_box_mammography_en_03-2014.png")
 grid.raster(img_fact)

```

```{r, echo=FALSE, results='asis'} 
#, results='asis'
for (z in 1:length(responses)) {
  cat(paste0(responses[z]))
}
```


### New-paradigm

```{r, echo=FALSE, results='asis'} 
img_new <- readPNG("materials/Presentation format/New-paradigm/brochure_new_young.png")
 grid.raster(img_new)

```

```{r, echo=FALSE, results='asis'} 
for (z in 1:length(responses)) {
  cat(paste0(responses[z]))
}
```