# FINAL ITEMS - Dictionary

* Problems context:
    + ca: breast cancer
    + pr: pregnant trisomy 21
* Presentation format:
    + nfab: Natural Frequency absolute
    + prab: Probability absolute
    + prre: Probability relative
    + pfab: Positive framework
* Normative PPV:
    + low: low ppv (33%)
    + high: high ppv (66%)
* Response type:
    + gi: global intuitive
    + gs: global systematic
    + sg: sequential guided
    + ss: sequential simple
    
# Breast Cancer

## Low normative PPV

### NF ABSOLUTE

```{r, results='asis', echo=FALSE, ca_nfab_low}
invisible(lapply(items_to_use_responses[grep("ca_nfab_low", items_to_use_responses)], function(x) cat(x, sep = "\n****************************\n")))
```

### PR ABSOLUTE

```{r, results='asis', echo=FALSE, ca_prab_low}
invisible(lapply(items_to_use_responses[grep("ca_prab_low", items_to_use_responses)], function(x) cat(x, sep = "\n****************************\n")))
```

### PR RELATIVE

```{r, results='asis', echo=FALSE, ca_prre_low}
invisible(lapply(items_to_use_responses[grep("ca_prre_low", items_to_use_responses)], function(x) cat(x, sep = "\n****************************\n")))
```

### PF ABSOLUTE

```{r, results='asis', echo=FALSE, ca_pfab_low}
invisible(lapply(items_to_use_responses[grep("ca_pfab_low", items_to_use_responses)], function(x) cat(x, sep = "\n****************************\n")))
```

## High normative PPV

### NF ABSOLUTE

```{r, results='asis', echo=FALSE, ca_nfab_high}
invisible(lapply(items_to_use_responses[grep("ca_nfab_high", items_to_use_responses)], function(x) cat(x, sep = "\n****************************\n")))
```

### PR ABSOLUTE

```{r, results='asis', echo=FALSE, ca_prab_high}
invisible(lapply(items_to_use_responses[grep("ca_prab_high", items_to_use_responses)], function(x) cat(x, sep = "\n****************************\n")))
```

### PR RELATIVE

```{r, results='asis', echo=FALSE, ca_prre_high}
invisible(lapply(items_to_use_responses[grep("ca_prre_high", items_to_use_responses)], function(x) cat(x, sep = "\n****************************\n")))
```

### PF ABSOLUTE

```{r, results='asis', echo=FALSE, ca_pfab_high}
invisible(lapply(items_to_use_responses[grep("ca_pfab_high", items_to_use_responses)], function(x) cat(x, sep = "\n****************************\n")))

```


***********************
# Trisomy 21

## Low normative PPV

### NF ABSOLUTE

```{r, results='asis', echo=FALSE, pr_nfab_low}
invisible(lapply(items_to_use_responses[grep("pr_nfab_low", items_to_use_responses)], function(x) cat(x, sep = "\n****************************\n")))
```

### PR ABSOLUTE

```{r, results='asis', echo=FALSE, pr_prab_low}
invisible(lapply(items_to_use_responses[grep("pr_prab_low", items_to_use_responses)], function(x) cat(x, sep = "\n****************************\n")))
```

### PR RELATIVE

```{r, results='asis', echo=FALSE, pr_prre_low}
invisible(lapply(items_to_use_responses[grep("pr_prre_low", items_to_use_responses)], function(x) cat(x, sep = "\n****************************\n")))
```

### PF ABSOLUTE

```{r, results='asis', echo=FALSE, pr_pfab_low}
invisible(lapply(items_to_use_responses[grep("pr_pfab_low", items_to_use_responses)], function(x) cat(x, sep = "\n****************************\n")))
```

## High normative PPV

### NF ABSOLUTE

```{r, results='asis', echo=FALSE, pr_nfab_high}
invisible(lapply(items_to_use_responses[grep("pr_nfab_high", items_to_use_responses)], function(x) cat(x, sep = "\n****************************\n")))
```

### PR ABSOLUTE

```{r, results='asis', echo=FALSE, pr_prab_high}
invisible(lapply(items_to_use_responses[grep("pr_prab_high", items_to_use_responses)], function(x) cat(x, sep = "\n****************************\n")))
```

### PR RELATIVE

```{r, results='asis', echo=FALSE, pr_prre_high}
invisible(lapply(items_to_use_responses[grep("pr_prre_high", items_to_use_responses)], function(x) cat(x, sep = "\n****************************\n")))
```

### PF ABSOLUTE

```{r, results='asis', echo=FALSE, pr_pfab_high}
invisible(lapply(items_to_use_responses[grep("pr_pfab_high", items_to_use_responses)], function(x) cat(x, sep = "\n****************************\n")))
```

*************************
# Pictorial presentation formats

## Fact-box item

```{r, echo=FALSE} 
fact_box_dir <- "materials/Presentation format/Fact-boxs/complete_factboxs/"

fact_box_imgs <- dir(fact_box_dir)
# image_read(paste0(fact_box_dir,fact_box_imgs[1]))

factbox_01 <- readPNG(paste0(fact_box_dir,fact_box_imgs[1]))
grid.raster(factbox_01)

```

```{r, echo=FALSE, results='asis'} 
#, results='asis'
for (z in 1:length(responses)) {
  cat(paste0(responses[z]))
}
```


## New-paradigm

```{r, echo=FALSE, results='asis'} 
new_padarigm_dir <- "materials/Presentation format/New-paradigm/brochure_complete/"

new_padarigm_imgs <- dir(new_padarigm_dir)

newparadigm_01 <- readPNG(paste0(new_padarigm_dir, new_padarigm_imgs))
grid.raster(newparadigm_01)

```

```{r, echo=FALSE, results='asis'} 
for (z in 1:length(responses)) {
  cat(paste0(responses[z]))
}
```