<!-- render("checklist_manual_changes.Rmd") -->

```{r, packages, echo=FALSE}
# Packages
if (!require('pacman')) install.packages('pacman'); library('pacman')
p_load(tidyverse, kableExtra)
```

```{r, kableME_func, echo=FALSE}
source("functions/kableMe.R")
scale_names <- read_csv("materials/Scales/scale_names.csv", col_types = "cccic")
```


# Qualtrics manual changes  

This is a checklist with all necessary manual changes to be done once the Qualtrics Survey is fully imported.

## Screening blocks (PPV item + Follow-up)

### Sliders

Change question type to Slider. On each question select the green button on the right upper corner and select Slider.

_Screening blocks_

```{r, table01, echo=FALSE}
tibble(check = "", 
       qIDs = c("will_Q02_01", paste0("com_Q", sprintf("%02d", 1:8),"_01"), 
                "fu_Q02_01", "fu_Q03_01", "fu_Q05_01", "fu_Q06_01", paste0("sevEmo_0", 1:6, "_01"), "will_Q02_02", paste0("com_Q", sprintf("%02d", 1:8),"_02"), 
                "fu_Q02_02", "fu_Q03_02", "fu_Q05_02", "fu_Q06_02", paste0("sevEmo_0", 1:6, "_01")),
       extra = c("", rep("", 8), "", "After change to Slider, __Select__ Allow Text Entry on 'Other' subitem", "", "Change max value to 10, and decimals to 1", rep("", 5), "", rep("", 8), "", "", "After change to Slider, __Select__ Allow Text Entry on 'Other' subitem", "", "Change max value to 10, and decimals to 1", rep("", 6))) %>% 
  kableME(.)
```

### Force response & Answer validation  

On each question, check the box "Force Response" (on the right contextual banner). In some cases an extra "Validation Type" has to be included. To do so, select one of the options below _Validation Options_.

_Block 01_

```{r, table02, echo=FALSE}
tibble(check = "",
       qIDs = c("ppv_gi_01", "ppv_gs_01", "ppv_sg01_01", "ppv_sg02_01", "ppv_sg03_01", "ppv_sg04_01", "ppv_ss01_01", "ppv_ss02_01"), 
       extra = c("", "__Validation type__: Content Validation, Number (min: 0, max: 100)", "__Validation type__: Content Validation, Number", "__Validation type__: Content Validation, Number", "__Validation type__: Content Validation, Number", "__Validation type__: Content Validation, Number", "__Validation type__: Content Validation, Number", "__Validation type__: Content Validation, Number")) %>% 
  bind_rows(., tibble(check = "",
                      qIDs = c("will_Q01_01", "will_Q02_01"), 
                      extra = (""))) %>% 
  bind_rows(., tibble(check = "",
                      qIDs = paste0("com_Q", sprintf("%02d", 1:8),"_01"), 
                      extra = (""))) %>% 
  bind_rows(., tibble(check = "",
                      qIDs = c(paste0("fu_Q0", 1:6, "_01")), 
                      extra = (""))) %>%
  bind_rows(., tibble(check = "",
                      qIDs = c(paste0("sevEmo_0", 1:6, "_01")), 
                      extra = (""))) %>%
  kableME(.)


```

_Block 02_

```{r, table03, echo=FALSE}
tibble(check = "",
       qIDs = c("ppv_gi_02", "ppv_gs_02", "ppv_sg01_02", "ppv_sg02_02", "ppv_sg03_02", "ppv_sg04_02", "ppv_ss01_02", "ppv_ss02_02"), 
       extra = c("", "__Validation type__: Content Validation, Number (min: 0, max: 100)", "__Validation type__: Content Validation, Number", "__Validation type__: Content Validation, Number", "__Validation type__: Content Validation, Number", "__Validation type__: Content Validation, Number", "__Validation type__: Content Validation, Number", "__Validation type__: Content Validation, Number")) %>% 
  bind_rows(., tibble(check = "",
                      qIDs = c("will_Q01_02", "will_Q02_02"), 
                      extra = (""))) %>% 
  bind_rows(., tibble(check = "",
                      qIDs = paste0("com_Q", sprintf("%02d", 1:8),"_02"), 
                      extra = (""))) %>% 
  bind_rows(., tibble(check = "",
                      qIDs = c(paste0("fu_Q0", 1:6, "_01")), 
                      extra = (""))) %>% 
  bind_rows(., tibble(check = "",
                      qIDs = c(paste0("sevEmo_0", 1:6, "_02")), 
                      extra = (""))) %>%
  kableME(.)
```


### Display logic

On each question, by right-clicking (or by clicking on the cog on the left side of the question), select _Add Display Logic..._. A pop-up window will open.

_Block 01_

```{r, table04, echo=FALSE}
tibble(check = "",
       qIDs = c("ppv_q_02_01", "ppv_gi_01", "ppv_gs_01", "ppv_sg01_01", "ppv_sg02_01", "ppv_sg03_01", "ppv_sg04_01", "ppv_ss01_01", "ppv_ss02_01", "fu_Q05_01", "fu_Q06_01", "com_Q08_01_01", "com_Q08_02_01", "com_Q08_03_01"),
       extra = c("_Embedded Data_ > _press_format_ > _Is Not Equal to_ > __pfab__ & _Embedded Data_ > _resp_type_ > _Is Not Equal to_ > __sg__", "_Embedded Data_ > _resp_type_ > _Is Equal to_ > __gi__",  "_Embedded Data_ > _resp_type_ > _Is Equal to_ > __gs__",  "_Embedded Data_ > _resp_type_ > _Is Equal to_ > __sg__", "_Embedded Data_ > _resp_type_ > _Is Equal to_ > __sg__", "_Embedded Data_ > _resp_type_ > _Is Equal to_ > __sg__", "_Embedded Data_ > _resp_type_ > _Is Equal to_ > __sg__", "_Embedded Data_ > _resp_type_ > _Is Equal to_ > __ss__", "_Embedded Data_ > _resp_type_ > _Is Equal to_ > __ss__", "_Question_ > _fu_Q01_01_ > __No__ > _Is Selected_", "_Question_ > _fu_Q01_01_ > __Yes__ > _Is Selected_", "_Embedded Data_ > _press_format_ > _Is NOT Equal to_ > __prab__ and __prre__" , "_Embedded Data_ > _press_format_ > _Is Equal to_ > __prab__ and __prre__", "_Embedded Data_ > _press_format_ > _Is Equal to_ > __prab__ or __prre__")) %>% 
  kableME(.)
```

_Block 02_

```{r, table05, echo=FALSE}
tibble(check = "",
       qIDs = c("ppv_q_02_02", "ppv_gi_02", "ppv_gs_02", "ppv_sg01_02", "ppv_sg02_02", "ppv_sg03_02", "ppv_sg04_02", "ppv_ss01_02", "ppv_ss02_02", "fu_Q05_02", "fu_Q06_02", "com_Q08_01_01", "com_Q08_02_01", "com_Q08_03_01"),
       extra = c("_Embedded Data_ > _press_format_ > _Is Not Equal to_ > __pfab__ & _Embedded Data_ > _resp_type_ > _Is Not Equal to_ > __sg__", "_Embedded Data_ > _resp_type_ > _Is Equal to_ > __gi__",  "_Embedded Data_ > _resp_type_ > _Is Equal to_ > __gs__",  "_Embedded Data_ > _resp_type_ > _Is Equal to_ > __sg__", "_Embedded Data_ > _resp_type_ > _Is Equal to_ > __sg__", "_Embedded Data_ > _resp_type_ > _Is Equal to_ > __sg__", "_Embedded Data_ > _resp_type_ > _Is Equal to_ > __sg__", "_Embedded Data_ > _resp_type_ > _Is Equal to_ > __ss__", "_Embedded Data_ > _resp_type_ > _Is Equal to_ > __ss__", "_Question_ > _fu_Q01_02_ > __No__ > _Is Selected_", "_Question_ > _fu_Q01_02_ > __Yes__ > _Is Selected_", "_Embedded Data_ > _press_format_ > _Is NOT Equal to_ > __prab__ and __prre__" , "_Embedded Data_ > _press_format_ > _Is Equal to_ > __prab__ and __prre__", "_Embedded Data_ > _press_format_ > _Is Equal to_ > __prab__ or __prre__")) %>% 
  kableME(.)
```

### Text entry size  

Reduce text entry size to minimum by dragging the rightmost side all the way to the left.

_Block 01_

```{r, table06, echo=FALSE}
tibble(check = "",
       qIDs = c("ppv_gs_01", "ppv_sg01_01", "ppv_sg02_01", "ppv_sg03_01", "ppv_sg04_01", "ppv_ss01_01", "ppv_ss02_01" ),
       extra = c("")) %>% 
  kableME(.)
```

_Block 02_

```{r, table07, echo=FALSE}
tibble(check = "",
       qIDs = c("ppv_gs_02", "ppv_sg01_02", "ppv_sg02_02", "ppv_sg03_02", "ppv_sg04_02", "ppv_ss01_02", "ppv_ss02_02" ),
       extra = c("")) %>% 
  kableME(.)
```

### Add JavaScript

On each question, by right-clicking (or by clicking on the cog on the left side of the question), select _Add JavaScript_. A pop-up window will open. Copy the JS code from the text files (_plain_text/js_codes/complete_) and paste them to the correspondent questions. Remember to select all when copying and when pasting over the JS template.

_Block 01_

```{r, table08, echo=FALSE}
tibble(check = "",
       qIDs = c("ppv_gi_01", "ppv_gs_01", "ppv_sg01_01", "ppv_ss01_01"),
       extra = c("From file: __gi_01_js_complete.txt__", "From file: __gs_01_js_complete.txt__", "From file: __sg_01_js_complete.txt__", "From file: __ss_01_js_complete.txt__")) %>%
  bind_rows(., tibble(check = "",
                      qIDs = c("will_Q01_01", "fu_Q01_01"), 
                      extra = c("From file: __will_should_she_01_js_complete.txt__", "From file: __fu_should_she_01_js_complete.txt__"))) %>% 
  bind_rows(., tibble(check = "",
                      qIDs = c("com_Q08_01_01", "com_Q08_03_01"), 
                      extra = c("From file: __ss_01_js_complete.txt__", "From file: __gs_01_js_complete.txt__"))) %>% 
  kableME(.)
```

_Block 02_

```{r, table09, echo=FALSE}
tibble(check = "",
       qIDs = c("ppv_gi_02", "ppv_gs_02", "ppv_sg01_02", "ppv_ss01_02"),
       extra = c("From file: __gi_02_js_complete.txt__", "From file: __gs_02_js_complete.txt__", "From file: __sg_02_js_complete.txt__", "From file: __ss_02_js_complete.txt__")) %>% 
  bind_rows(., tibble(check = "",
                      qIDs = c("will_Q01_02", "fu_Q01_02"), 
                      extra = c("From file: __will_should_she_02_js_complete.txt__", "From file: __fu_should_she_02_js_complete.txt__"))) %>% 
  bind_rows(., tibble(check = "",
                      qIDs = c("com_Q08_01_02", "com_Q08_03_02"), 
                      extra = c("From file: __ss_01_js_complete.txt__", "From file: __gs_01_js_complete.txt__"))) %>% 
  kableME(.)
```

## Scales

### Force response & Answer validation  

_Abbreviated mathemathics anxiety rating scale_

```{r, echo=FALSE}
this <- filter(scale_names, long_name == "abbreviated_math_anxiety_rating_scale")

tibble(check = "",
       qIDs = paste0(this$short_name, "_", sprintf("%02d", seq(this$no_items))), 
       extra = "") %>%
  kableME(.)
```

_A priori screening belief_

```{r, echo=FALSE}
this <- filter(scale_names, long_name == "a_priori_screening_belief")

tibble(check = "",
       qIDs = paste0(this$short_name, "_", sprintf("%02d", seq(this$no_items))), 
       extra = "") %>%
  kableME(.)
```

_Beck Anxiety Inventory_

```{r, echo=FALSE}
this <- filter(scale_names, long_name == "beck_anxiety_inventory")

tibble(check = "",
       qIDs = paste0(this$short_name, "_", sprintf("%02d", seq(this$no_items))), 
       extra = "") %>%
  kableME(.)
```

_Big Five Inventory_

```{r, echo=FALSE}
this <- filter(scale_names, long_name == "big_five_inventory")

tibble(check = "",
       qIDs = paste0(this$short_name, "_", sprintf("%02d", seq(this$no_items))), 
       extra = "") %>%
  kableME(.)
```

_Cognitive Reflection Test 7-items_

```{r, echo=FALSE}
this <- filter(scale_names, long_name == "cognitive_reflection_test_7")

tibble(check = "",
       qIDs = paste0(this$short_name, "_", sprintf("%02d", seq(this$no_items))), 
       extra = "") %>%
  kableME(.)
```

_General Decision Making Style_

```{r, echo=FALSE}
this <- filter(scale_names, long_name == "general_decision_making_style")

tibble(check = "",
       qIDs = paste0(this$short_name, "_", sprintf("%02d", seq(this$no_items))), 
       extra = "") %>%
  kableME(.)
```

_Lipkus Numeracy Scale_

```{r, echo=FALSE}
this <- filter(scale_names, long_name == "lipkus_numeracy_scale")

tibble(check = "",
       qIDs = paste0(this$short_name, "_", sprintf("%02d", seq(this$no_items))), 
       extra = c(rep("Content Validation -> Number", 2), "Content Validation -> Number", rep("", 2), 
                 "Content Validation -> Number", "", rep("Content Validation -> Number", 2), "Content Validation -> Number",
                 rep("Content Validation -> Number", 1))) %>%
  kableME(.)
```

_Multiple Stimulus Types Ambiguity Tolerance Scale II_

```{r, echo=FALSE}
this <- filter(scale_names, long_name == "multiple_stim_types_ambiguity_tolerance_scale")

tibble(check = "",
       qIDs = paste0(this$short_name, "_", sprintf("%02d", seq(this$no_items))), 
       extra = "") %>%
  kableME(.)
```

_Need for Cognition_

```{r, echo=FALSE}
this <- filter(scale_names, long_name == "need_for_cognition")

tibble(check = "",
       qIDs = paste0(this$short_name, "_", sprintf("%02d", seq(this$no_items))), 
       extra = "") %>%
  kableME(.)
```

_Probabilistic Reasoning Scale_

```{r, echo=FALSE}
this <- filter(scale_names, long_name == "probabilistic_reasoning_scale")

tibble(check = "",
       qIDs = paste0(this$short_name, "_", sprintf("%02d", seq(this$no_items))), 
       extra = "") %>%
  kableME(.)
```

_Risk Avoidance Scale_

```{r, echo=FALSE}
this <- filter(scale_names, long_name == "risk_avoidance_scale")

tibble(check = "",
       qIDs = paste0(this$short_name, "_", sprintf("%02d", seq(this$no_items))), 
       extra = "") %>%
  kableME(.)
```

_Risk Propensity Scale_

```{r, echo=FALSE}
this <- filter(scale_names, long_name == "risk_propensity_scale")

tibble(check = "",
       qIDs = paste0(this$short_name, "_", sprintf("%02d", seq(this$no_items))), 
       extra = "") %>%
  kableME(.)
```

_Sociodemographic Scale_

```{r, echo=FALSE}
this <- filter(scale_names, long_name == "sociodemographic_scale")

tibble(check = "",
       qIDs = paste0(this$short_name, "_", c("gen", "age", "edu", "lan", "nat")), 
       extra = "") %>%
  kableME(.)
```

_Subjective Numeracy Scale_

```{r, echo=FALSE}
this <- filter(scale_names, long_name == "subjective_numeracy_scale")

tibble(check = "",
       qIDs = paste0(this$short_name, "_", sprintf("%02d", seq(this$no_items))), 
       extra = "") %>%
  kableME(.)
```

_Tolerance of Ambiguity_

```{r, echo=FALSE}
this <- filter(scale_names, long_name == "tolerance_of_ambiguity")

tibble(check = "",
       qIDs = paste0(this$short_name, "_", sprintf("%02d", seq(this$no_items))), 
       extra = "") %>%
  kableME(.)
```

### Text entry size  

Reduce text entry size to minimum by dragging the rightmost side all the way to the left.

_Lipkus Numeracy Scale_

```{r, echo=FALSE}
this <- filter(scale_names, long_name == "lipkus_numeracy_scale")

tibble(check = "",
       qIDs = paste0(this$short_name, "_", sprintf("%02d", seq(this$no_items)[!seq(this$no_items) %in% c(3,4,5)])), 
       extra = c("")) %>% 
  kableME(.)
```

### Randomization

```{r, echo=FALSE}
this <- filter(scale_names, long_name == "shared_decision_making")

tibble(check = "",
       qIDs = paste0(this$short_name, "_", sprintf("%02d", seq(this$no_items)[!seq(this$no_items) %in% c(3,4,5)])), 
       extra = c("Randomize choices")) %>% 
  kableME(.)

```


## Others

### Force response & Answer validation

_Previous Experience_

```{r, echo=FALSE}
tibble(check = "",
       qIDs = paste0("prevExp", "_", sprintf("%02d", seq(4))), 
       extra = c("")) %>% 
  kableME(.)
```

_Survey Effort_

```{r, echo=FALSE}
tibble(check = "",
       qIDs = paste0("eff", "_", sprintf("%02d", seq(2))), 
       extra = c("")) %>% 
  kableME(.)
```
