<!-- render("checklist_manual_changes.Rmd") -->

```{r, packages, echo=FALSE}
# Packages
if (!require('pacman')) install.packages('pacman'); library('pacman')
p_load(kableExtra)
```

```{r, kableME_func, echo=FALSE}
kableME <- function(some_table) {
some_table %>%  
  mutate(no = seq(nrow(.))) %>% select(no, names(.)) %>% 
  kable() %>% kable_styling(., "striped")
}
```
### Force response & Answer validation  

Check the box "Force Response" for each of the following questions. In some cases an extra "Validation Type" has to be included.

_Block 01_

```{r, table02, echo=FALSE}
tibble(check = "",
       qIDs = c("ppv_Q_gi_01", "ppv_Q_gs_01", "ppv_Q_sg01_01", "ppv_Q_sg02_01", "ppv_Q_sg03_01", "ppv_Q_sg04_01", "ppv_Q_ss01_01", "ppv_Q_ss02_01"), 
       extra = c("", "__Validation type__: Content Validation, Number (min: 0, max: 100)", "__Validation type__: Content Validation, Number", "__Validation type__: Content Validation, Number", "__Validation type__: Content Validation, Number", "__Validation type__: Content Validation, Number", "__Validation type__: Content Validation, Number", "__Validation type__: Content Validation, Number")) %>% 
  bind_rows(., tibble(check = "",
                      qIDs = c("wilScre_Q01_01", "wilScre_Q02_01"), 
                      extra = (""))) %>% 
  bind_rows(., tibble(check = "",
                      qIDs = c("fu_Q01_01", "fu_Q02_01", "fu_Q03_01", "fu_Q04_01", "fu_Q05_01"), 
                      extra = (""))) %>%
  kableME(.)
```

_Block 02_

```{r, table03, echo=FALSE}
tibble(check = "",
       qIDs = c("ppv_Q_gi_02", "ppv_Q_gs_02", "ppv_Q_sg01_02", "ppv_Q_sg02_02", "ppv_Q_sg03_02", "ppv_Q_sg04_02", "ppv_Q_ss01_02", "ppv_Q_ss02_02"), 
       extra = c("", "__Validation type__: Content Validation, Number (min: 0, max: 100)", "__Validation type__: Content Validation, Number", "__Validation type__: Content Validation, Number", "__Validation type__: Content Validation, Number", "__Validation type__: Content Validation, Number", "__Validation type__: Content Validation, Number", "__Validation type__: Content Validation, Number")) %>% 
  bind_rows(., tibble(check = "",
                      qIDs = c("wilScre_Q01_02", "wilScre_Q02_02"), 
                      extra = (""))) %>% 
  bind_rows(., tibble(check = "",
                      qIDs = c("fu_Q01_02", "fu_Q02_02", "fu_Q03_02", "fu_Q04_02", "fu_Q05_02"), 
                      extra = (""))) %>% 
  kableME(.)
```


### Display logic

_Block 01_

```{r, table04, echo=FALSE}
tibble(check = "",
       qIDs = c("ppv_Q_gi_01", "ppv_Q_gs_01", "ppv_Q_sg01_01", "ppv_Q_sg02_01", "ppv_Q_sg03_01", "ppv_Q_sg04_01", "ppv_Q_ss01_01", "ppv_Q_ss02_01", "fu_Q05_01 (1st slider)", "fu_Q05_01 (2nd slider)"),
       extra = c("_Embedded Data_ > _resp_type_ > _Is Equal to_ > __gi__",  "_Embedded Data_ > _resp_type_ > _Is Equal to_ > __gs__",  "_Embedded Data_ > _resp_type_ > _Is Equal to_ > __sg__", "_Embedded Data_ > _resp_type_ > _Is Equal to_ > __sg__", "_Embedded Data_ > _resp_type_ > _Is Equal to_ > __sg__", "_Embedded Data_ > _resp_type_ > _Is Equal to_ > __sg__", "_Embedded Data_ > _resp_type_ > _Is Equal to_ > __ss__", "_Embedded Data_ > _resp_type_ > _Is Equal to_ > __ss__", "_Question_ > _fu_Q01_01_ > __No__ > _Is Selected_", "_Question_ > _fu_Q01_01_ > __Yes__ > _Is Selected_")) %>% 
  kableME(.)
```

_Block 02_

```{r, table05, echo=FALSE}
tibble(check = "",
       qIDs = c("ppv_Q_gi_02", "ppv_Q_gs_02", "ppv_Q_sg01_02", "ppv_Q_sg02_02", "ppv_Q_sg03_02", "ppv_Q_sg04_02", "ppv_Q_ss01_02", "ppv_Q_ss02_02", "fu_Q05_02 (1st slider)", "fu_Q05_02 (2nd slider)"),
       extra = c("_Embedded Data_ > _resp_type_ > _Is Equal to_ > __gi__",  "_Embedded Data_ > _resp_type_ > _Is Equal to_ > __gs__",  "_Embedded Data_ > _resp_type_ > _Is Equal to_ > __sg__", "_Embedded Data_ > _resp_type_ > _Is Equal to_ > __sg__", "_Embedded Data_ > _resp_type_ > _Is Equal to_ > __sg__", "_Embedded Data_ > _resp_type_ > _Is Equal to_ > __sg__", "_Embedded Data_ > _resp_type_ > _Is Equal to_ > __ss__", "_Embedded Data_ > _resp_type_ > _Is Equal to_ > __ss__", "_Question_ > _fu_Q01_02_ > __No__ > _Is Selected_", "_Question_ > _fu_Q01_02_ > __Yes__ > _Is Selected_")) %>% 
  kableME(.)
```

### Text entry size  

Reduce text entry size to minimum by draging the rightmost side all the way to the left.

_Block 01_

```{r, table06, echo=FALSE}
tibble(check = "",
       qIDs = c("ppv_Q_gs_01", "ppv_Q_sg01_01", "ppv_Q_sg02_01", "ppv_Q_sg03_01", "ppv_Q_sg04_01", "ppv_Q_ss01_01", "ppv_Q_ss02_01" ),
       extra = c("")) %>% 
  kableME(.)
```

_Block 02_

```{r, table07, echo=FALSE}
tibble(check = "",
       qIDs = c("ppv_Q_gs_02", "ppv_Q_sg01_02", "ppv_Q_sg02_02", "ppv_Q_sg03_02", "ppv_Q_sg04_02", "ppv_Q_ss01_02", "ppv_Q_ss02_02" ),
       extra = c("")) %>% 
  kableME(.)
```

### Add JavaScript

Copy JS code from txt files and add them to the correspondent questions. Select All within the txt file and paste it over all the dafault content of the Add JavaScript pop-up window.

_Block 01_

```{r, table08, echo=FALSE}
tibble(check = "",
       qIDs = c("ppv_Q_gi_01", "ppv_Q_gs_01", "ppv_Q_sg01_01", "ppv_Q_ss01_01"),
       extra = c("From file: __gi_01_js_complete.txt__", "From file: __gs_01_js_complete.txt__", "From file: __sg_01_js_complete.txt__", "From file: __ss_01_js_complete.txt__")) %>% 
  kableME(.)
```

_Block 02_

```{r, table09, echo=FALSE}
tibble(check = "",
       qIDs = c("ppv_Q_gi_02", "ppv_Q_gs_02", "ppv_Q_sg01_02", "ppv_Q_ss01_02"),
       extra = c("From file: __gi_02_js_complete.txt__", "From file: __gs_02_js_complete.txt__", "From file: __sg_02_js_complete.txt__", "From file: __ss_02_js_complete.txt__")) %>% 
  kableME(.)
```
