--- 
title: "Experiment 1 - Conditions creation "
author: ""
date: "`r Sys.Date()`"
site: bookdown::bookdown_site
output: bookdown::gitbook
documentclass: book
bibliography: [book.bib, packages.bib]
biblio-style: apalike
link-citations: yes
github-repo: rstudio/bookdown-demo
description: "Conditions creation"
---


```{r}
# Clean enviroment
rm(list = ls(all=TRUE))
```

# Experiment design 

Independent Variables

* Presentation format (between subjects):
    + Natural frequencies (absolute)
    + Probabilities (absolute)
    + Probabilities (relative)
    + Positive Framework (absolute)
    + New paradigm (pictorial)
    + Fact-box (pictorial)

* Response type
    + [global-sistemática]  x %  
    + [global-intuitiva] muy baja (0-20%), baja ](21-40%), intermedia (41-60%), alta (61-80%), muy alta (81-100%)
    + [secuencial-simple] x out of y  
    + [secuencial-guiada] y tendrán mamografía + y cáncer. y tendrán mamografía + y no cáncer. Por lo tanto, x de cada y tendrán cáncer


## Dictionary

* Problems context:
    + ca: breast cancer
    + pr: pregnant trisomy 21
* Presentation format:
    + nfab: Natural Frequency absolute
    + prab: Probability absolute
    + prre: Probability relative
    + pfab: Positive framework absolute
    + fbpi: Factbox pictorial
    + nppi: New-paradigm pictorial
* Normative PPV:
    + low: low ppv (33%)
    + high: high ppv (66%)
* Response type:
    + gi: global intuitive
    + gs: global systematic
    + sg: sequential guided
    + ss: sequential simple
    
    
## Scales

* A priori screening belief
* Beck anxiety inventory
* Big five inventory
* Cognitive reflection test 7-items multiple choice
* General decision making style
* Abbreviated mathematics anxiety rating scale
* Multiple stimulus types ambiguity tolerance scale II
* Need for cognition
* Lipkus numeracy scale
* Probabilistic reasoning scale
* Risk avoidance scale
* Risk_propensity_scale
* Severity and emotional reaction
* Sociodemographic scale
* Subjective numeracy scale
* Tolerance of ambiguity

```{r include=FALSE}
# automatically create a bib database for R packages
knitr::write_bib(c(
.packages(), 'bookdown', 'knitr', 'rmarkdown'
), 'packages.bib')
```