--- 
title: "Conditions creation"
author: "Nico"
date: "`r Sys.Date()`"
site: bookdown::bookdown_site
output: bookdown::gitbook
documentclass: book
bibliography: [book.bib, packages.bib]
biblio-style: apalike
link-citations: yes
github-repo: rstudio/bookdown-demo
description: "Conditions creation"
---

```{r}
# Clean enviroment
rm(list = ls(all=TRUE))
```

```{r}
# Packages
if (!require('pacman')) install.packages('pacman'); library('pacman')
p_load(tidyverse, png, grid)
```

```{r}
# Functions
# to put numbers into problems
source("function_numbers2problems.R")

```

# Items + pregunta

## Items

### Text-only items
```{r, read_txt_items_into_a_list}
# path to responses folder
tx_items_dir <- "materials/Presentation format/Text-items/"

# responses files
tx_item_files <- dir(tx_items_dir, pattern = ".txt")

# paths to each response file
tx_item_files_path <- paste0(tx_items_dir, tx_item_files)

# list with responses as char strings
tx_items <- lapply(tx_item_files_path, 
                    function(x) readChar(con = x, nchars = file.info(x)$size))

# assing name to each response type
names(tx_items) <- gsub(".txt", "", tx_item_files)


```

### Positive framework items

```{r, read_pofr_items_into_a_list}
# path to responses folder
pf_items_dir <- "materials/Presentation format/Positive-framework/"

# responses files
pf_item_files <- dir(pf_items_dir, pattern = ".txt")

# paths to each response file
pf_item_files_path <- paste0(pf_items_dir, pf_item_files)

# list with responses as char strings
pf_items <- lapply(pf_item_files_path, 
                    function(x) readChar(con = x, nchars = file.info(x)$size))

# assing name to each response type
names(pf_items) <- gsub(".txt", "", pf_item_files)

# items to problems
problems <- c(tx_items, pf_items)

```


### Textual items

```{r, results='asis', echo=FALSE, print_items}
# items to problems
for (i in 1:length(problems)) {
  print(names(problems[i]))
  cat(paste0(problems[i]))
}

```

# Numbers sets
```{r}
# read csv with number
numbers_item <-
  read_csv("materials/Numbers/numbers_bayes.csv", col_types = cols())

```


```{r}
numbers_item
```


# Create items

## Create items (combine items with numbers)
```{r}
numbers2problems(problems)
# problems_numbered %>% str

```

## Items to use: 

```{r, echo=FALSE}

# Final items
items_to_use <-
c(
problems_numbered[[1]][[1]],
problems_numbered[[2]][[3]],
problems_numbered[[2]][[5]],
problems_numbered[[3]][[1]],
problems_numbered[[4]][[2]]
)
```

```{r}
# PRINT ITEMS
invisible(sapply(items_to_use, cat))
```

# Respuesta
```{r}

# path to responses folder
response_types_dir <- "materials/Response_type/"

# responses files
response_type_files <- dir(response_types_dir)

# paths to each response file
response_type_files_path <- paste0(response_types_dir, response_type_files)

# list with responses as char strings
responses <- lapply(response_type_files_path, 
                    function(x) readChar(con = x, nchars = file.info(x)$size))

# assing name to each response type
names(responses) <- gsub(".txt", "", response_type_files)

# Response types
responses

```

# Combine problem with questions
```{r}
problems2responses(items_to_use, "items_to_use")
```


## Text-only NATURAL FREQUENCIES ABSOLUTE (high)

```{r, results='asis', echo=FALSE, text_only_nfab}
x=1

for (x in 1:length(responses)) {
  
  cat(
    paste0(
      names(
        items_to_use_responses[[1]][[x]]
        ), " ***********************************\n\n"))
  cat(
    paste0(
      items_to_use_responses[[1]][[x]]
      )
    )

}

```

## Text-only NATURAL FREQUENCIES ABSOLUTE (low)

```{r, results='asis', echo=FALSE}

for (x in 1:length(responses)) {
  
  cat(paste0(names(items_to_use_responses[[2]][[x]]),  " ***********************************\n\n"))
  cat(paste0(items_to_use_responses[[2]][[x]]))

}

```

## Text-only PROBABILITIES ABSOLUTE

```{r, results='asis', echo=FALSE}

for (x in 1:length(responses)) {
  
  cat(paste0(names(items_to_use_responses[[3]][[x]]), " ***********************************\n\n"))
  cat(paste0(items_to_use_responses[[3]][[x]]))

}

```

## Positive-framework

```{r, results='asis', echo=FALSE}

for (x in 1:length(responses)) {
  
  cat(paste0(names(items_to_use_responses[[4]][[x]]), " ***********************************\n\n"))
  cat(paste0(items_to_use_responses[[4]][[x]]))

}

```

## Pictorial presentation formats

**What questions to use with this conditions.**
**Reliability & What it is more probable given a positive result, having or not having the disease. If this two questions are asked to every condition we can compare them**
**Reliability: how gringos understand this question**

### Fact-box item

```{r, echo=FALSE} 
img_fact <- readPNG("materials/Presentation format/Fact-boxs/fact_box_mammography_en_03-2014.png")
 grid.raster(img_fact)

```

```{r, echo=FALSE} 
#, results='asis'
for (z in 1:length(responses)) {
  cat(paste0(responses[z]))
}
```


### New-paradigm

```{r, echo=FALSE} 
img_new <- readPNG("materials/Presentation format/New-paradigm/brochure_new_young.png")
 grid.raster(img_new)

```

```{r, echo=FALSE} 
for (z in 1:length(responses)) {
  cat(paste0(responses[z]))
}
```




```{r include=FALSE}
# automatically create a bib database for R packages
knitr::write_bib(c(
.packages(), 'bookdown', 'knitr', 'rmarkdown'
), 'packages.bib')
```