--- 
title: "Experiment 1 - Conditions creation "
author: ""
date: "`r Sys.Date()`"
site: bookdown::bookdown_site
output: bookdown::gitbook
documentclass: book
bibliography: [book.bib, packages.bib]
biblio-style: apalike
link-citations: yes
github-repo: rstudio/bookdown-demo
description: "Conditions creation"
---


```{r}
# Clean enviroment
rm(list = ls(all=TRUE))
```

```{r}
# Packages
if (!require('pacman')) install.packages('pacman'); library('pacman')
p_load(tidyverse, magick, png, grid)
```

```{r}
# Functions
# to put numbers into problems
source("functions/numbers2problems.R")

```

# Experiment design 

TODO: Brief description about the experiment design (as it should be in a paper)

Independent Variables

* Presentación de información:
    + FN absolutas
    + Probabilidades absolutas
    + Probabilidades relativas
    + Positive framework
    + Nuevo paradigma
    + Fact-box

* Response type
    + [global-sistemática]    x %  
    + [global-intuitiva] muy baja, baja, intermedia, alta, muy alta
    + [secuencial-simple]   x   de cada   y  
    + [secuencial-guiada]  y   tendrán mamografía + y cáncer.   y   tendrán mamografía + y no cáncer. Por lo tanto,   x   de cada   y   tendrán cáncer

* Riesgo de la prueba diagnóstica
    + Grave (consecuencias negativas irreversibles)
    + Leve (cierto riesgo de consecuencias negativas negligibles)
    + TODO: USE TWO DIFFERENT PROBABILITIES: relatively high/low probs (e.g. 1% vs 5/10% ???)
    
    

## TODO:

* Fix number sets
    + (PROB) The difference between high/low is now only FP
    + (FREQ) Numbers change but proportions are the same

* Prepare/improve New paradigm (CHECK NEW SHORT BROCHURE)

* Positive Framework es en chances y SINGLE-EVENTS!
    + Esto causa problemas con las preguntas
    + Transformar PF a non-single event, o al reves?
    
* PF
    + La pregunta en PF es entre irrelevante y molesta
    + Of those that receive a positive result, how many would you expect to have breast cancer?
    + La dejamos?

* Prob absolute
    + In the problem each piece of information, except the prevalence, is phrased relatively to another piece of information, and not to the sample. e.g. x% of those pregnant with a fetus… should be:
x% (of those) are women pregnant with a fetus with Trisomy 21 (will) that receive a positive test result.

* All presentation formats
    + To make textual and pictorial items comparable we have to introduce questions like this (aren't this questions the same thing?):
        + How reliable is the test?
        + If a women receive a positive test result, how probable is that she actually has breast cancer/is pregnant with a fetus with Trisomy 21?
      



```{r include=FALSE}
# automatically create a bib database for R packages
knitr::write_bib(c(
.packages(), 'bookdown', 'knitr', 'rmarkdown'
), 'packages.bib')
```