--- 
title: "Conditions creation"
author: "Nico"
date: "`r Sys.Date()`"
site: bookdown::bookdown_site
output: bookdown::gitbook
documentclass: book
bibliography: [book.bib, packages.bib]
biblio-style: apalike
link-citations: yes
github-repo: rstudio/bookdown-demo
description: "Conditions creation"
---


```{r}
# Clean enviroment
rm(list = ls(all=TRUE))
```

```{r}
# Packages
if (!require('pacman')) install.packages('pacman'); library('pacman')
p_load(tidyverse, png, grid)
```

```{r}
# Functions
# to put numbers into problems
source("function_numbers2problems.R")

```

# Items + pregunta

## Items

### Text-only items
```{r, read_txt_items_into_a_list}
# path to responses folder
tx_items_dir <- "materials/Presentation format/Text-items/"

# responses files
tx_item_files <- dir(tx_items_dir, pattern = ".txt")

# paths to each response file
tx_item_files_path <- paste0(tx_items_dir, tx_item_files)

# list with responses as char strings
tx_items <- lapply(tx_item_files_path, 
                    function(x) readChar(con = x, nchars = file.info(x)$size)) 

# assing name to each response type
names(tx_items) <- gsub(".txt", "", tx_item_files)


```

### Positive framework items

```{r, read_pofr_items_into_a_list}
# path to responses folder
pf_items_dir <- "materials/Presentation format/Positive-framework/"

# responses files
pf_item_files <- dir(pf_items_dir, pattern = ".txt")

# paths to each response file
pf_item_files_path <- paste0(pf_items_dir, pf_item_files)

# list with responses as char strings
pf_items <- lapply(pf_item_files_path, 
                    function(x) readChar(con = x, nchars = file.info(x)$size))

# assing name to each response type
names(pf_items) <- gsub(".txt", "", pf_item_files)

# items to problems
problems <- c(tx_items, pf_items)

```


### Textual items

```{r, results='asis', echo=FALSE, print_items}
# items to problems
for (i in 1:length(problems)) {
  print(names(problems[i]))
  cat(paste0(problems[i]))
}

```

# Numbers sets
+ Combine every context with every set?
+ Two number sets (NF, PR). If we convert NF to PR we only get one set of numbers per normative PPV.

```{r}
# read csv with number
numbers_item <-
  read_csv("materials/Numbers/numbers_bayes.csv", col_types = cols())

```


```{r}
numbers_item
```


# Create items

## Create items (combine items with numbers)
```{r}
numbers2problems(problems)
# problems_numbered %>% str

```

## Items to use: 

```{r, echo=FALSE}

# Final items
items_to_use <-
c(
problems_numbered[[1]][[1]],
problems_numbered[[2]][[3]],
problems_numbered[[2]][[5]],
problems_numbered[[3]][[1]],
problems_numbered[[4]][[2]]
)
```

```{r}
# PRINT ITEMS
invisible(sapply(items_to_use, cat))
```

# Respuesta
```{r}

# path to responses folder
response_types_dir <- "materials/Response_type/"

# responses files
response_type_files <- dir(response_types_dir)

# paths to each response file
response_type_files_path <- paste0(response_types_dir, response_type_files)

# list with responses as char strings
responses <- lapply(response_type_files_path, 
                    function(x) readChar(con = x, nchars = file.info(x)$size))

# assing name to each response type
names(responses) <- gsub(".txt", "", response_type_files)

# Response types
invisible(lapply(responses, cat))

```

# Combine problem with questions

```{r}
# WORKING (LOOPS)

items_to_use_responses <- 
lapply(items_to_use, function(x) 
  paste0(x, lapply(responses, paste0)))

responses_names <- names(responses)

for (problem_loop in 1:length(items_to_use_responses)) {
# problem_loop=1  
  for (item_loop in 1:length(items_to_use_responses[[problem_loop]])) {
    # item_loop=1
    
    items_to_use_responses[[problem_loop]][[item_loop]] <- 
      gsub("([w|h]_)\n", paste0("\\1",responses_names[item_loop], "\n"), items_to_use_responses[[problem_loop]][[item_loop]])
  
    }
  
}

```

```{r}
invisible(
  lapply(
    items_to_use_responses, function(x) {cat(x, sep = "")}
  )
)

```

# FINAL ITEMS

**Original sequential-guided question:**  
Therefore, there are ______ chance(s) that her positive test result correctly indicates the presence of the anomaly, and there are ____ chance(s) that her positive test result incorrectly indicates the presence of the anomaly. (Pighin, 2017)  
**Ours:**  
______ people receive a positive test result that correctly indicates the presence of the anomaly, and ____ people receive a positive test result that incorrectly indicates the presence of the anomaly.


## Text-only NATURAL FREQUENCIES ABSOLUTE (low)

```{r, results='markup', echo=FALSE, text_only_nfab_high}

invisible(lapply(items_to_use_responses[1], function(x) cat(x, sep = "\n****************************\n")))

```

## Text-only PROBABILITIES ABSOLUTE (low)

```{r, results='markup', echo=FALSE, text_only_prab_low}

invisible(lapply(items_to_use_responses[2], function(x) cat(x, sep = "\n****************************\n")))

```

## Text-only PROBABILITIES RELATIVE (low)

```{r, results='markup', echo=FALSE, text_only_prrl_low}

invisible(lapply(items_to_use_responses[3], function(x) cat(x, sep = "\n****************************\n")))

```

## POSITIVE FRAMEWORK (high)

```{r, results='markup', echo=FALSE, text_only_pf_high}

invisible(lapply(items_to_use_responses[4], function(x) cat(x, sep = "\n****************************\n")))

```

## Pictorial presentation formats

**What questions to use with this conditions.**
**Reliability & What it is more probable given a positive result, having or not having the disease. If this two questions are asked to every condition we can compare them**
**Reliability: how gringos understand this question**

### Fact-box item

```{r, echo=FALSE, results='asis'} 
img_fact <- readPNG("materials/Presentation format/Fact-boxs/fact_box_mammography_en_03-2014.png")
 grid.raster(img_fact)

```

```{r, echo=FALSE, results='asis'} 
#, results='asis'
for (z in 1:length(responses)) {
  cat(paste0(responses[z]))
}
```


### New-paradigm

```{r, echo=FALSE, results='asis'} 
img_new <- readPNG("materials/Presentation format/New-paradigm/brochure_new_young.png")
 grid.raster(img_new)

```

```{r, echo=FALSE, results='asis'} 
for (z in 1:length(responses)) {
  cat(paste0(responses[z]))
}
```

# TODO:

+ fix number sets


```{r include=FALSE}
# automatically create a bib database for R packages
knitr::write_bib(c(
.packages(), 'bookdown', 'knitr', 'rmarkdown'
), 'packages.bib')
```