--- 
title: "Experiment 1 - Conditions creation "
author: ""
date: "`r Sys.Date()`"
site: bookdown::bookdown_site
output: bookdown::gitbook
documentclass: book
bibliography: [book.bib, packages.bib]
biblio-style: apalike
link-citations: yes
github-repo: rstudio/bookdown-demo
description: "Conditions creation"
---


```{r}
# Clean enviroment
rm(list = ls(all=TRUE))
```

```{r}
# Packages
if (!require('pacman')) install.packages('pacman'); library('pacman')
p_load(tidyverse, magick, png, grid)
```

```{r}
# Functions
# to put numbers into problems
source("functions/numbers2problems.R")

```

# Experiment design 

TODO: Brief description about the experiment design (as it should be in a paper)

Independent Variables

* Presentation format:
    + Natural frequencies (absolutes)
    + Probabilities (absolutes)
    + Probabilities (relatives)
    + New paradigma
    + Fact-box
    + Positive Framework

* Response type
    + [global-sistemática]    x %  
    + [global-intuitiva] muy baja, baja, intermedia, alta, muy alta
    + [secuencial-simple]   x   de cada   y  
    + [secuencial-guiada]  y   tendrán mamografía + y cáncer.   y   tendrán mamografía + y no cáncer. Por lo tanto,   x   de cada   y   tendrán cáncer

* Riesgo de la prueba diagnóstica
    + Probabilidad de problemas (Aborto/Infeccion que deriva en necesidad de mastectomia)
        + Alta (10%)
        + Baja (1%)
    + NO vamos a manipular el tipo de problemas (Grave (consecuencias negativas irreversibles), Leve (cierto riesgo de consecuencias negativas reversibles / negligibles))


## TODO:

* Check follow-up test text: See point 7 in the book.

* Sequential guided (sg) question: The original question (pighin not pighin) says "anomaly". Now we use anomaly for both, breast cancer and trisomy 21. Adapt question to each context?

* Scales for (Check /Experimento 1/R_conditions_creation/scales/potential_questions.odt):
    + Actitud hacia aborto
    + Actitud hacia trisomia 21
    + Mastectomia
    + Cancer

* Fix number sets
    + PPVs ~.2 & ~.8
    + Numbers should be the "same" in PRabs, FNabs, PF abs??? (this will solve the following point?) 
    + (PROB) The difference between high/low is now only FP
    + OK? - (FREQ) Numbers change but proportions are the same  

* All presentation formats
    + To make textual and pictorial items comparable we have to introduce questions like this (aren't this questions the same thing?):
        + Preguntas razonables para Fact-box: p(SALVARSE|screening) & p(DAÑO|screening)
        + Para nuevo paradigma???
        + How reliable is the test?
        + If a woman receives a positive test result, how probable is that she actually has breast cancer/is pregnant with a fetus with Trisomy 21?

* Fact-box and New paradigm
    + (GORKA & NICO): Check content of cancer new-paradigm (Experimento 1/R_conditions_creation/materials/Presentation_format/nppi) and pregnant factbox (Experimento 1/R_conditions_creation/materials/Presentation_format/fbpi)
      
* (NICO) Better way to reorder items (Reorder items)?

* (DONE) Fix sequential guided (sg) question, add "Therefore...".

* (DONE) Include contexts for the problems (finally we used McNair's (2014) formulation, no women mentioned in the information pieces. Only in the instructions.)
    + Should we include "women" in each problem sentence? (e.g. 5 in every 100 women have breast cancer at the time of the screening. 4 in every 5 of those women with breast cancer will receive a positive mammogram.)
        + Also, include "women" in the questions? (e.g. Of those women that receive positive mamographies...)

* (DONE) Transformamos Positive Framework a non-single-events (A woman -> Women)



```{r include=FALSE}
# automatically create a bib database for R packages
knitr::write_bib(c(
.packages(), 'bookdown', 'knitr', 'rmarkdown'
), 'packages.bib')
```